\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1,T2A]{fontenc}
\usepackage[english,russian]{babel}
\usepackage[margin=1.2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{helvet}

\renewcommand{\familydefault}{\sfdefault}

\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt}
\titlespacing*{\section}{0pt}{3ex plus 1ex minus .2ex}{1ex plus .2ex}
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]

\begin{document}
\pagestyle{empty}

\begin{center}
    {\huge \textbf{Semyon Khodus}}\\[0.2cm]
    simon.khodus@gmail.com $|$ +43 677 620 79 187 $|$ Klagenfurt am Wörthersee, Austria\\[0.1cm]
    \href{https://linkedin.com/in/semyon-khodus}{linkedin.com/in/semyon-khodus} $|$ \href{https://github.com/sflvrr}{github.com/sflvrr}
\end{center}

\vspace{0.3cm}

\section{Education}
\noindent
\textbf{University of Klagenfurt} \hfill Oct 2025 -- June 2028\\
Robotics and AI \hfill GPA: 1.0/1.0\\[0.15cm]
\textbf{Higher School of Economics (HSE)} \hfill Sept 2025 -- June 2029\\
Computer Science, Mathematics, and Machine Learning \hfill GPA: 8.66/10.00

\section{Experience}
\noindent
\textbf{IPG Photonics (VPG Laserone)} $|$ \textit{Researcher} \hfill July 2024 -- Aug 2024
\begin{itemize}
    \item Researched optical crystal growth processes, resulting in the development of a new optimized growth methodology.
    \item Documented experimental conditions and prepared progress reports utilizing specialized chemical compounds and software tools.
\end{itemize}

\vspace{0.15cm}
\noindent
\textbf{Freelance} $|$ \textit{Mathematics, Physics \& IT Tutor} \hfill 2023 -- Present
\begin{itemize}
    \item Prepared students for advanced university entrance exams and olympiads.
    \item Taught complex mathematical concepts in English, developing custom programming curricula to strengthen logic and problem-solving skills.
\end{itemize}

\section{Projects \& Leadership}
\noindent
\textbf{StudMan} $|$ \textit{Backend Developer} \hfill 2025 -- Present
\begin{itemize}
    \item Architecting an AI-powered tool for generating educational flashcards.
\end{itemize}

\vspace{0.15cm}
\noindent
\textbf{UniBot \& MoscowFace} $|$ \textit{Lead Developer} \hfill 2024 -- 2025
\begin{itemize}
    \item Engineered a Telegram bot (Python, BeautifulSoup4) to track and automate university admissions deadline updates.
    \item Developed a containerized guide bot (Docker, aiogram) aimed at challenging cultural stereotypes.
\end{itemize}

\vspace{0.15cm}
\noindent
\textbf{Student Leadership Teams} $|$ \textit{Team \& Group Leader} \hfill 2022 -- Present
\begin{itemize}
    \item Coordinated team workflows, resolved internal conflicts, and represented student groups in faculty negotiations to optimize the educational process.
\end{itemize}

\section{Technical Skills}
\noindent
\textbf{Languages:} Python, C++, Go, Swift, JavaScript, HTML, LaTeX\\
\textbf{Technologies \& Tools:} Docker, PostgreSQL, SQLite, SQLAlchemy, Flask, FastAPI, PyQt5, Spark, Streamlit\\
\textbf{Data Science:} ML/NLP models, NumPy, Pandas, Matplotlib, Seaborn, Plotly

\section{Languages \& Interests}
\noindent
\textbf{Spoken Languages:} Russian (Native), English (C1), German (B1), Italian (A1), Norwegian (A1)\\
\textbf{Interests:} Medical Engineering, Music Creating, Botanics
\end{document}